SIR Model With Testing Flows and Isolation

### 2021-01-12 codes/sir_macpan.Rnw
minutes added

\begin{document}
By Ali Gharouni,
<<date,echo=F>>=
Sys.time()
@
This is my a test for MacPan package.

@@

@@

>>>>

\begin{document}
By Ali Gharouni,
<<date,echo=F>>=
Sys.time()
@
This is my a test for MacPan package in 2 steps:
- step 1: simulate a simple SIR model and recover the results by specifying the parameters of MacPan.
- step 2: Read COVID19-Canada data from Mike's repo, estimate the transmision rate beta(t) and do projection.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Step 1, SIR and MacPan}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Step 2, Data and MacPan}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<Read Data from Mike's repo, echo=T>>=
library(readr)

covid_url <- "https://raw.githubusercontent.com/wzmli/COVID19-Canada/master/git_push/clean.Rout.csv"
df_covid <- read_csv(covid_url)

plot_pos_prov <- ggplot(df_covid,aes(x=Date,y=confirmed_positive,col=Province))+
                  geom_point()

direct.label(plot_pos_prov,"last.bumpup")
